---
title: '2019_06_Bell_RDMWorkingGroup'
author: "Emma Bell"
date: '2019-06-24'
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    number_sections: yes
    toc: yes
    toc_float: yes
subtitle: 'Analysis of cluster usage'
---

# Summary {.tabset}

This R Notebook contains code pertaining to the project 2019_06_Bell_RDMWorkingGroup.

* Aim: To understand how the De Carvalho lab uses our cluster space
* Objectives:
  * Which directories take up the most space?
  * Which users take up the most space?
  * What file types take up the most space?

# Set up

The parent directory for this project is `/path/to/base/dir`.

```{r}
base.dir <- file.path("/path/to/base/dir")
data.dir <- file.path(base.dir,"data")
docs.dir <- file.path(base.dir,"docs")
results.dir <- file.path(base.dir,"results")
```

All figures are outputted to the following specifications:

```{r}
units <- "cm"
res <- 480
pointsize <- 7
```

This R Notebook requires the following packages:

```{r}
library(viridis)
```

The colour scheme used in this R Notebook is as follows:

```{r}
pal <- inferno(n = 10, begin = 0.2, end = 0.8)
barplot(1:10, col = pal, border = NA)
```

# Analysis {.tabset}

## Analysis 1

## Analysis 2

## Analysis 3
